lnc34a splice junctions

### 2017-11-15 inst/suppFigure2b_stableLineCCND1exp/suppFigure2b_stableLineCCND1exp.Rmd
all supplementary and fig3 pdfs written

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = condition,
      y = log2fold
    ),
    trim = TRUE,
    alpha = 0.3,
    color = NA,
    fill = "gray",
    scale = "width"
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = condition,
      y = log2fold,
      fill = condition
    ),
    binwidth = 1/200,
    colour = NA,
    alpha = 0.5,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 4,
    show.legend = TRUE
  ) +
  geom_linerange(
    data = stats,
    aes(
      x = condition,
      ymin = CI95l,
      ymax = CI95h
    ),
    colour = "gray20"
  ) +
  geom_point(
    data = stats,
    aes(
      x = condition,
      y = mean
    ),
    colour = "gray20",
    size = 6,
    shape = 95
  ) +
  geom_segment(
    aes(
      x = 1,
      y = 0.175, 
      xend = 2,
      yend = 0.175
    ),
    colour = "grey43"
  ) +
  geom_label(
    data = stats,
    aes(
      x = 1.5,
      y = 0.19,
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 5,
    family = "Arial Unicode MS"
  ) +
  scale_y_continuous("\u0394\u0394Ct") +
  labs(
    x = "Cell line",
    title = "CCND1"
  ) +
  guides(fill = FALSE)

plotRmarkdown(p)

>>>>

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = condition,
      y = log2fold
    ),
    trim = TRUE,
    alpha = 0.3,
    color = NA,
    fill = "gray",
    scale = "width"
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = condition,
      y = log2fold,
      fill = condition
    ),
    binwidth = 1/200,
    colour = NA,
    alpha = 0.5,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 4,
    show.legend = TRUE
  ) +
  scale_y_continuous("\u0394\u0394Ct") +
  labs(
    x = "Cell line",
    title = "CCND1"
  ) +
  guides(fill = FALSE)

markdown <- p + 
  geom_linerange(
    data = stats,
    aes(
      x = condition,
      ymin = CI95l,
      ymax = CI95h
    ),
    colour = "gray20"
  ) +
  geom_point(
    data = stats,
    aes(
      x = condition,
      y = mean
    ),
    colour = "gray20",
    size = 6,
    shape = 95
  ) +
  geom_segment(
    aes(
      x = 1,
      y = 0.175, 
      xend = 2,
      yend = 0.175
    ),
    colour = "grey43"
  ) +
  geom_label(
    data = stats,
    aes(
      x = 1.5,
      y = 0.19,
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 5,
    family = "Arial Unicode MS"
  )

plotRmarkdown(markdown)

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = condition,
      ymin = CI95l,
      ymax = CI95h
    ),
    colour = "gray20",
    size = 0.1
  ) +
  geom_point(
    data = stats,
    aes(
      x = condition,
      y = mean
    ),
    colour = "gray20",
    shape = 95
  ) +
  geom_segment(
    aes(
      x = 1,
      y = 0.175, 
      xend = 2,
      yend = 0.175
    ),
    colour = "grey43",
    size = 0.1
  ) +
  geom_label(
    data = stats,
    aes(
      x = 1.5,
      y = 0.2,
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 2,
    family = "Arial Unicode MS"
  )

figure <- plotPDF(pdf)
path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2b_stableLineCCND1exp/suppFigure2b_stableLineCCND1exp.pdf"

#ggsave(
#  plot = figure, 
#  filename = path, 
#  device = cairo_pdf, 
#  height = 60,
#  width = 83,
#  units = "mm"
#)
```

### 2017-11-15 inst/suppFigure2c_stableLineCCND1prot/suppFigure2c_stableLineCCND1prot.Rmd
all supplementary and fig3 pdfs written

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = condition,
      y = log2fold
    ),
    trim = TRUE,
    alpha = 0.3,
    color = NA,
    fill = "gray",
    scale = "width",
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = condition,
      y = log2fold,
      fill = condition
    ),
    binwidth = 1/30,
    colour = NA,
    alpha = 0.5,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 4,
    show.legend = TRUE
  ) +
  geom_linerange(
    data = stats,
    aes(
      x = condition,
      ymin = CI95l,
      ymax = CI95h
    ),
    colour="gray20"
  ) +
  geom_point(
    data = stats,
    aes(
      x = condition,
      y = mean
    ),
    colour="gray20",
    size = 6,
    shape = 95
  ) +
  geom_segment(
    data = stats,
    aes(
      x = 1,
      y = max(CI95h) + 0.25,
      xend = 2,
      yend = max(CI95h) + 0.25
    ),
    colour="grey43"
  ) +
  geom_label(
    data = stats,
    aes(
      x = 1.5,
      y = max(CI95h) + 0.5,
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 5,
    family = "Arial Unicode MS"
  ) +
  scale_y_continuous("log2(Fold)") +
  labs(
    x = "Cell line",
    title = "CCND1 protein"
  ) +
  guides(fill = FALSE)

plotRmarkdown(p)

>>>>

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = condition,
      y = log2fold
    ),
    trim = TRUE,
    alpha = 0.3,
    color = NA,
    fill = "gray",
    scale = "width",
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = condition,
      y = log2fold,
      fill = condition
    ),
    binwidth = 1/30,
    colour = NA,
    alpha = 0.5,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 4,
    show.legend = TRUE
  ) +
  scale_y_continuous("log2(Fold)") +
  labs(
    x = "Cell line",
    title = "CCND1 protein"
  ) +
  guides(fill = FALSE)

markdown <- p +
  geom_point(
    data = stats,
    aes(
      x = condition,
      y = mean
    ),
    colour="gray20",
    size = 6,
    shape = 95
  ) +
  geom_segment(
    data = stats,
    aes(
      x = 1,
      y = max(CI95h) + 0.25,
      xend = 2,
      yend = max(CI95h) + 0.25
    ),
    colour="grey43"
  ) +
  geom_label(
    data = stats,
    aes(
      x = 1.5,
      y = max(CI95h) + 0.4,
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 5,
    family = "Arial Unicode MS"
  ) +
   geom_linerange(
    data = stats,
    aes(
      x = condition,
      ymin = CI95l,
      ymax = CI95h
    ),
    colour="gray20"
  )

plotRmarkdown(markdown)

pdf <- p + 
  geom_point(
    data = stats,
    aes(
      x = condition,
      y = mean
    ),
    colour="gray20",
    shape = 95
  ) +
  geom_segment(
    data = stats,
    aes(
      x = 1,
      y = max(CI95h) + 0.25,
      xend = 2,
      yend = max(CI95h) + 0.25
    ),
    colour="grey43",
    size = 0.1
  ) +
  geom_label(
    data = stats,
    aes(
      x = 1.5,
      y = max(CI95h) + 0.4,
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 2,
    family = "Arial Unicode MS"
  ) +
   geom_linerange(
    data = stats,
    aes(
      x = condition,
      ymin = CI95l,
      ymax = CI95h
    ),
    colour="gray20",
    size = 0.1
  )

figure <- plotPDF(pdf)
path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2c_stableLineCCND1prot/suppFigure2c_stableLineCCND1prot.pdf"
ggsave(
  plot = figure, 
  filename = path, 
  device = cairo_pdf, 
  height = 60,
  width = 83,
  units = "mm"
)
```

### 2017-11-15 inst/suppFigure2e_lnc34aSplJnc/suppFigure2e_lnc34aSplJnc.Rmd
all supplementary and fig3 pdfs written

```{r, fig.align='center', fig.height=8, fig.width=12}
###locus
p1 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = filter(data, feature == "exon"),
    aes(xmin = start, xmax = stop, y = gene, fill = gene),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    colour = "gray"
  ) +
  ggthemes::theme_few() +
  ggthemes::scale_fill_ptol() +
  geom_segment(
    data = filter(data, feature == "intron"),
    aes(x = start, xend = stop, y = gene, yend = gene),
    linetype = "dotted",
    colour = "gray",
    size = 1
  ) +
  xlim(9241000, 9257900) +
  labs(x = "Chromosome 1", y = "Genes") +
  guides(fill = FALSE)

@@

grobz <- lapply(list(p1, p2), ggplotGrob)
g <- rbind(grobz[[2]], grobz[[1]], size = "last")
grid.newpage()
grid.draw(resize_heights(g, unit(c(3,1), "null")))
```

>>>>

```{r, fig.align='center', fig.height=8, fig.width=12, warning = FALSE}
#plot rmarkdown
###locus
p1 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = filter(data, feature == "exon"),
    aes(xmin = start, xmax = stop, y = gene, fill = gene),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    colour = "gray"
  ) +
  ggthemes::theme_few() +
  ggthemes::scale_fill_ptol() +
  geom_segment(
    data = filter(data, feature == "intron"),
    aes(x = start, xend = stop, y = gene, yend = gene),
    linetype = "dotted",
    colour = "gray",
    size = 1
  ) +
  xlim(9241000, 9257900) +
  labs(x = "Chromosome 1", y = "Genes") +
  guides(fill = FALSE)

@@

grobz <- lapply(list(p1, p2), ggplotGrob)
g <- rbind(grobz[[2]], grobz[[1]], size = "last")
grid.newpage()
grid.draw(resize_heights(g, unit(c(3,1), "null")))

#plot pdf
#genes
p1 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = filter(data, feature == "exon"),
    aes(xmin = start, xmax = stop, y = gene, fill = gene),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    arrow_body_height = grid::unit(1, "mm"),
    colour = "gray",
    lwd = 0.1
  ) +
  ggthemes::theme_few() +
  ggthemes::scale_fill_ptol() +
  geom_segment(
    data = filter(data, feature == "intron"),
    aes(x = start, xend = stop, y = gene, yend = gene),
    linetype = "dotted",
    colour = "gray",
    size = 0.25
  ) +
  xlim(9241000, 9257900) +
  labs(x = "Chromosome 1", y = "Genes") +
  guides(fill = FALSE) +
  theme(
    axis.text = element_text(size = 3),
    axis.title.x = element_text(size = 4),
    axis.title.y = element_text(size = 4, margin = margin(r = 8, "cm")),
    axis.ticks.length = unit(0.5, "mm"),
    axis.ticks = element_line(size = 0.15),
    panel.border = element_rect(fill = NA, size = 0.1),
    plot.margin = unit(c(0.01, 1, 0.01, 1), "mm")
  )

#splice junctions
p2 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = splJnc,
    aes(xmin = start, xmax = stop, y = y, fill = n),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    arrow_body_height = unit(2, "pt"),
    colour = NA,
    lwd = 0.1,
    show.legend = TRUE
  ) +
  ggthemes::theme_few() +
  viridis::scale_fill_viridis() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 4),
    legend.position = "top",
    legend.title = element_text(size = 4),
    legend.text = element_text(size = 4),
    legend.box.spacing = unit(3, "pt"),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.border = element_rect(fill = NA, size = 0.1),
    plot.margin = unit(c(0.01, 1, 0.01, 1), "mm"),
    strip.text.y = element_text(angle = 0)
  ) +
  labs(y = "Cage reads") +
  xlim(9241000, 9257900) +
  guides(fill = guide_colourbar(
    title = "Reads",
    title.position = "top",
    title.hjust = 0.5,
    barheight = unit(4, "pt"),
    barwidth = unit(40, "pt")
  ))

grobz <- lapply(list(p1, p2), ggplotGrob)
g <- rbind(grobz[[2]], grobz[[1]], size = "last")
g <- resize_heights(g, unit(c(6, 1), "null"))

path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2e_lnc34aSplJnc/suppFigure2e_lnc34aSplJnc.pdf"
ggsave(
  plot = g, 
  filename = path, 
  device = cairo_pdf, 
  height = 60,
  width = 83,
  units = "mm"
)

```
